---
title: "Add HCRIS data"
format: html
editor: visual
embed-resources: true
---

## Setup

Load necessary libraries:

```{r}
library(tidyverse)
library(tidyr)
library(dplyr)
library(janitor)
library(ggplot2)
library(hrbrthemes)
library(GGally)
library(tabulator)
library(readxl)
library(broom)
library(plm)
library(openxlsx)
library(purrr)
```

Load in manually cleaned data set:

```{r}
Manual_matched <- read_excel("Data_manual_cleaning.xlsx", 
    sheet = "Deleted non matched", skip = 2)
View(Manual_matched)
```

Load in NASHP ownership data:

```{r}
NASHP <- read_excel("NASHP HCT Data 2024 July.xlsx", 
    sheet = "Downloadable")
View(NASHP)
```

Filter NASHP data to focus on New York.

```{r}

cleaned_NASHP <- NASHP %>% filter(State == "NY") 
```

R sometimes throws errors due to the complexity of the NASHP data set. In order to prevent future loading and crashing problems I write the filtered data set so I have a backup for potential use in future. Name new csv file cleanNASHP in the data folder under Thesis GU.

```{r}
write.csv(cleaned_NASHP, "C:/Users/Mitchell/Documents/Thesis GU/Data/cleanNASHP.csv")
print(cleaned_NASHP)
```

Exploring cleaned NASHP data.

```{r}
View(cleaned_NASHP %>% count(`Hospital Ownership Type`))

for_viz <-(cleaned_NASHP %>% group_by(Year) %>% count(`Hospital Ownership Type`))
```

Visualize hospital ownership count by year.

```{r}
for_viz %>% ggplot(mapping = aes(x = `Hospital Ownership Type`, fill = Year, y = n)) + geom_bar(position = "dodge", stat = "identity") 

```

Trying to do a percent bar chart. Not successful yet.

```{r}
for_viz %>% ggplot(mapping = aes(x = `Hospital Ownership Type`, fill = Year, y = n)) + geom_bar(position = "fill", stat = "identity") +   scale_color_gradient2(low = "blue", high = "orange") 
```

\*Grouped line chart.

```{r}
for_viz %>% ggplot(mapping = aes(x = Year, group = `Hospital Ownership Type`, y = n, color = `Hospital Ownership Type`)) +
  geom_line() + scale_y_continuous(breaks = seq(0, 175, by = 25)) + theme_minimal()
```

Merge manually cleaned set to cleaned NASHP data set by CCN.

```{r}
ccn_cleaned_NASHP <- cleaned_NASHP %>% rename( ccn = `CCN#`) %>% transform(ccn= as.numeric(ccn))

Combined <- full_join(x = Manual_matched,
          y = ccn_cleaned_NASHP,
          by = "ccn",
          copy = FALSE,
          keep = NULL) %>% clean_names()
```

Load SPARCS data set

```{r}

library(readr)
ppc_rates <- read_csv("All_Payer_Inpatient_Major_Potentially_Preventable_Complication__PPC__Rates_by_Hospital__SPARCS___Beginning_2013_20241001.csv")
View(ppc_rates)
```

Merging SPARCS data set to NASHP and Manual matched. Use right join to maintain the additional years of observations not present in ppc_rates data.

\[right_join

by argument c("facility","year")\]

```{r}
ppc_rates_janitor <- ppc_rates %>% clean_names() %>% rename( year = discharge_year)

SPARCS_combined <- right_join(x = ppc_rates_janitor,
                             y = Combined,
                             by = c("facility_id", "year"),
                             copy = FALSE,
                             keep = NULL)
```

Add in AHRQ cross sectional data sets. Note documentation shows that coding is not standardized between years. For instance a 2 in hospital ownership in 2022 is a public or governmental hospital while in 2020 a 2 means church-operated. Only 2021 includes 4 equals federal.

```{r}
AHRQ2022 <- read_excel("AHRQ datasets/chsp-hospital-linkage-2022-rev.xlsx")
View(AHRQ2022)

Cleaned2022 <- AHRQ2022 %>% filter(hospital_state == "NY")

graphed2022 <- Cleaned2022 %>% count(is.na(hos_ownership)) %>% mutate(logic = `is.na(hos_ownership)`)

ggplot(graphed2022, aes(x=logic, y=n)) + geom_bar(stat = "identity", position = "dodge")

Cleanedmore2022 <- Cleaned2022 %>% mutate(year = case_when(
  hospital_state == "NY" ~ 2022
)) %>% mutate(hos_ownership = case_when(
  hos_ownership == 1 ~ "Non-Profit",
  hos_ownership == 2 ~ "Governmental",
  hos_ownership == 3 ~ "Church-Operated",
  hos_ownership == 5 ~ "For-Profit"
  )) %>% transform(ccn = as.double(ccn))


#^recode var hos_ownership so the number are characters. 

AHRQ2021 <- read_excel("AHRQ datasets/chsp-hospital-linkage-2021-rev.xlsx")
View(AHRQ2021)

Cleaned2021 <- AHRQ2021 %>% filter(hospital_state == "NY") %>% mutate(year = case_when(
  hospital_state == "NY" ~ 2021
)) %>% mutate(hos_ownership = case_when(
  hos_ownership == 1 ~ "Non-Profit",
  hos_ownership == 2 ~ "Church-Operated",
  hos_ownership == 3 ~ "Governmental",
  hos_ownership == 4 ~ "Federal",
  hos_ownership == 5 ~ "For-Profit"
  )) %>% transform(ccn = as.double(ccn))

#^recode var hos_ownership so the number are characters. 

AHRQ2020 <- read_excel("AHRQ datasets/chsp-hospital-linkage-2020-rev.xlsx")
View(AHRQ2020)

Cleaned2020 <- AHRQ2020 %>% filter(hospital_state == "NY") %>% mutate(year = case_when(
  hospital_state == "NY" ~ 2020
)) %>% mutate(hos_ownership = case_when(
  hos_ownership == 1 ~ "Non-Profit",
  hos_ownership == 2 ~ "Church-Operated",
  hos_ownership == 3 ~ "Governmental",
  hos_ownership == 5 ~ "For-Profit"
  )) %>% transform(ccn = as.double(ccn))
```

Combine AHRQ cross-sectional data with already combined data sets (NASHP/SPARCS/Manually Cleaned).

```{r}
Fully_combined <- left_join(
  x = SPARCS_combined,
  y = Cleanedmore2022,
  by = c("ccn", "year"),
  copy = FALSE,
  keep = NULL) 

Fully_combined <- left_join(
  x = Fully_combined,
  y = Cleaned2021,
  by = c("ccn", "year"),
  copy = FALSE,
  keep = NULL)

Fully_combined <- left_join(
  x = Fully_combined,
  y = Cleaned2020,
  by = c("ccn", "year"),
  copy = FALSE,
  keep = NULL)
```

Write fully combined data set to excel as a backup and for my advisor.

```{r}
write.xlsx(Fully_combined, 'Fully_combined_dataset.xlsx')
```

## Add County Data
```{r}

```

