---
title: "Post Manual Match"
author: "Mitchell Zupko"
format: html
editor: visual
warning: false
embed-resources: true
---

## Code

Load necessary libraries:

```{r}
library(tidyverse)
library(tidyr)
library(dplyr)
library(janitor)
library(ggplot2)
library(hrbrthemes)
library(GGally)
library(tabulator)
```

Load in manually cleaned data set:

```{r}
library(readxl)
Manual_matched <- read_excel("Data_manual_cleaning.xlsx", 
    sheet = "Deleted non matched", skip = 2)
View(Manual_matched)
```

Add second tibble which is the original AHRQ data:

```{r}
library(readr)
AHRQdata <- read_csv("chsp-hospital-linkage-2021-rev.csv")
View(AHRQdata)
```

Group by and filter AHRQ data using dplyr library. Filter AHRQ data to just NY hospitals.

```{r}
NY_ahrq_data <- AHRQdata %>% group_by(hospital_state) %>%
  filter(hospital_state == "NY") %>% ungroup()
```

Add third tibble which is original SPARCS data:

```{r}
library(readr)
ppc_rates <- read_csv("All_Payer_Inpatient_Major_Potentially_Preventable_Complication__PPC__Rates_by_Hospital__SPARCS___Beginning_2013_20241001.csv")
View(ppc_rates)

```

Clean names as part of janitor package.

```{r}
ppc_rates_clean <- ppc_rates %>% clean_names()
```

Joining data sets together. Mutating joins also use dplyr library.

```{r}
first_match <- left_join(Manual_matched,
                         NY_ahrq_data,
                         by = join_by(compendium_hospital_id),
                         keep = NULL)

first_match_clean <- first_match %>% clean_names()

ppc_rates_column <- ppc_rates_clean %>% rename_at('hospital_name', ~'hospital_name_sparcs')
```

```{r}
second_match <- left_join(first_match_clean,
                        ppc_rates_column,
                        by = join_by(hospital_name_sparcs),
                        keep = NULL)
```

Mean and Median for the difference in discharges variable.

```{r}
mean(second_match$difference_in_discharges)
median(second_match$difference_in_discharges)
```

Count of hospital ownership values.

```{r}
second_match %>% group_by(hos_ownership) %>% count() 
```

Histogram of hospital ownership using ggplot (looks more like a bar graph here though).

```{r}

second_match %>%
  ggplot(aes(x=hos_ownership)) +
  geom_histogram( binwidth = .5,fill="#69b3a2", color="#e9ecef", alpha=0.9) +
  theme_minimal() +
  xlab("Hospital Ownership Type") +
  ylab("Number of Hospitals") +
  labs(
    title = "Hospital Ownership Type in New York State from 2013-2021"  
  )
```

Determining number of hospitals in SPARCS.

```{r}
Sparcs_count <- ppc_rates_clean %>% group_by(hospital_name) %>% count()
```

Scatter plot looking at hospital ownership and difference in discharges using ggplot with a loess line.

```{r}
ggplot(second_match, aes(x=hos_ownership, y=difference_in_discharges)) + geom_point() +
  geom_smooth(method = "loess", se =FALSE) +
  theme_minimal() +
  xlab("Hospital Ownership") +
  ylab("Difference in Discharges") +
  ggtitle("Variation in Potentially Preventable Complications Greatest in Non-Profits")
```

Correlations using Pearson's method:

```{r}
cor(second_match$hos_ownership, second_match$difference_in_discharges, 
    use = 'complete.obs')

cor(second_match$hos_net_revenue, second_match$difference_in_discharges, 
    use = 'complete.obs')

cor(second_match$hos_majteach, second_match$difference_in_discharges, 
    use = 'complete.obs')

cor(second_match$hos_beds, second_match$difference_in_discharges, 
    use = 'complete.obs')

cor(second_match$hos_dsch, second_match$difference_in_discharges, 
    use = 'complete.obs')

cor(second_match$hos_res, second_match$difference_in_discharges, 
    use = 'complete.obs')

cor(second_match$hos_highuc, second_match$difference_in_discharges, 
    use = 'complete.obs')
```

Tabulator library for quantiles and tabcounts.

```{r}
tab_match <- second_match %>% tab(hos_ownership, difference_in_discharges)

second_match %>% tabcount(hos_ownership, difference_in_discharges)

second_match %>% quantiles(difference_in_discharges) 
```

Drop unused columns from data set.

```{r}
remove_cols <- c('compendium_hospital_id', 'ccn_x', 'hospital_name_ahrq', 
                 'hospital_city_x', 'hospital_name_sparcs', 'facility_id.x',
                 'mitchell_id', 'ccn_y', 'hospital_street', 'hospital_city_y',
                 'hospital_state', 'hospital_zip', 'acutehosp_flag', 'health_sys_id',
                 'health_sys_name', 'health_sys_city', 'health_sys_state',
                 'hos_children', 'hos_vmajteach', 'hos_teachint', 'hos_highdpp',
                 'facility_id.y','ppc_version')

second_match_minvariables <- subset(second_match,
                                    select = !(names(second_match) %in% remove_cols))
```

Correlation graphic using the ggally package.

```{r}
second_match_minvariables %>% ggcorr(method = c("pairwise", "pearson"),
                        geom = "tile")
```
