---
title: "Thesis Data Cleaning"
format: html
editor: visual
author: Mitchell Zupko
---

## Thesis Data Cleaning

## Cleaning Code

Load in necessary libraries for manipulating and visualizing data:

```{r}
library(readr)
library(tidyverse)
library(tidyr)
library(dplyr)
library(janitor)
library(ggplot2)
library(hrbrthemes)
library(GGally)
```

Load in dataset one from AHRQ compendium of U.S. Health systems, 2021:

```{r}
AHRQdata <- read_csv("chsp-hospital-linkage-2021-rev.csv")
View(AHRQdata)
```

Group by and filter are both dplyr commands.

```{r}
NY_ahrq_data <- AHRQdata %>% 
  group_by(hospital_state) %>%
  filter(hospital_state == "NY") %>% ungroup()
```

Adding second tibble/data frame from NY SPARCS data on potentially preventable complications.

```{r}
ppc_rates <- read_csv("All_Payer_Inpatient_Major_Potentially_Preventable_Complication__PPC__Rates_by_Hospital__SPARCS___Beginning_2013_20241001.csv")
View(ppc_rates)
```

Clean names is part of janitor package.

```{r}
ppc_rates_clean <- ppc_rates %>% clean_names()

```

Mutating joins also dplyr command.

```{r}
NYwithPPC2 <- left_join(ppc_rates_clean,
                        NY_ahrq_data,
                        by = join_by(hospital_name),
                        keep = NULL,
                        multiple = "first")
```

Count of hospital ownership values. Roughly 500 with close to 1100 NAs. Figure out why...

```{r}
NYwithPPC2 %>% group_by(hos_ownership) %>% count() 

```

Scatter plot uses ggplot

```{r}
ggplot(NYwithPPC2, aes(x=hos_ownership, y=difference_in_discharges)) + geom_point()

```

Density graph uses ggplot and hrbrthemes customization.

```{r}
NYwithPPC2 %>% ggplot(aes(x=hos_ownership)) +
  geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)
```

Hospital Ownership Count original AHRQ.

```{r}
NY_ahrq_data %>% group_by(hos_ownership) %>% count()

```

Correlation matrix using ggally package.

```{r}
NYwithPPC2 %>% ggcorr(method = c("pairwise", "pearson"),
                        geom = "tile")
```

Correlation in cleaned data using pearson, spearman, and kendall correlation.

```{r}
cor(NYwithPPC2$hos_ownership, NYwithPPC2$difference_in_discharges, 
    use = 'complete.obs')

cor(NYwithPPC2$hos_ownership, NYwithPPC2$difference_in_discharges,
    method='spearman' ,use = 'complete.obs')

cor(NYwithPPC2$hos_ownership, NYwithPPC2$difference_in_discharges,
    method='kendall' ,use = 'complete.obs')
```

Pearson =

```         
-0.05171849
```

Spearman =

```         
 -0.03505024
```

Kendall =

```         
-0.02796712
```

Pivot wider requires the tidyr package. Look at ppc rates clean correlation by year.

```{r}
wide_ppc_clean <- ppc_rates_clean %>% pivot_wider(names_from = discharge_year,
                                names_sep = ".", 
                                values_from = difference_in_discharges)

wide_ppc_clean %>% ggcorr(method = c("pairwise", "pearson"),
                        geom = "tile")

cor(wide_ppc_clean[, c('2013','2014','2015','2016','2017','2018',
                       '2019','2020','2021')])
```

Lets try privot wider in ppc rates clean by hospital.

```{r}
wide_ppc_clean2 <- ppc_rates_clean %>% pivot_wider(names_from = hospital_name,
                                                  names_sep = ".", 
                                                  values_from = c(difference_in_discharges))  

view(wide_ppc_clean2)
```

Too many created variables to examine although there appears to be variation within hospital by year but possibly not variation across all hospitals in the state combined by year.
